# Week 4

## Requirements

-   [Input the data sets](https://drive.google.com/drive/folders/1Xec-soCTIomk_DfagSOu3awfuDrCrk6j?usp=sharing)

-   Join the data sets together based on their common field

-   Remove any fields you don't need for the challenge

-   Change the weekdays from separate columns to one column of weekdays and one of the pupil's travel choice

-   Group the travel choices together to remove spelling mistakes

-   Create a Sustainable (non-motorised) vs Non-Sustainable (motorised) data field 

    -   Scooters are the child type rather than the motorised type

-   Total up the number of pupil's travelling by each method of travel 

-   Work out the % of trips taken by each method of travel each day

    -   Round to 2 decimal places

-   [Output the data](https://drive.google.com/file/d/1XkzXuk4ZZYiRWW2eT65Pup2hE1kXUIxF/view?usp=sharing)

::: callout-warning
## % of Trips Taken

Although we are being asked for the percent, the output shows the fraction. For consistency, we show the fraction.
:::

## Setup

```{r}
#| message: false
library(tidyverse)
raw_1 <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1SXZMY-kVx2Dz5q3DoFtqO7JRr3u8rGRF_-vE0lwii3I")
raw_2 <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/18tBSHiZFM51u5X5WZYyXHSqI0vC1REscBSs1KJ4S37c")
```

## EDA

::: panel-tabset
## Table 1

```{r}
#| echo: false
raw_1
```

## Summary 1

```{r}
#| echo: false
skimr::skim(raw_1)
```

## Table 2

```{r}
#| echo: false
raw_2
```

## Summary 2

```{r}
#| echo: false
skimr::skim(raw_2)
```
:::

## Preppin

```{r}
output <- raw_2 |>
  pivot_longer(-`Student ID`,
               names_to = "Weekday",
               values_to = "Method of Travel") |>
  mutate(
    `Method of Travel` = case_match(
      `Method of Travel`,
      "Bycycle" ~ "Bicycle",
      "Carr" ~ "Car",
      c("Scootr", "Scoter") ~ "Scooter",
      c("Walkk", "Wallk", "WAlk", "Waalk") ~ "Walk",
      "Helicopeter" ~ "Helicopter",
      .default = `Method of Travel`
    ),
    `Sustainable?` = case_match(
      `Method of Travel`,
      c("Bicycle", "Dad's Shoulders", "Hopped", "Jumped", 
        "Mum's Shoulders", "Scooter", "Skipped", "Walk") ~ "Sustainable",
      .default = "Non-Sustainable"
      )
  ) |> 
  count(`Sustainable?`, `Method of Travel`, Weekday, name = "Number of Trips") |> 
  add_count(Weekday, wt = `Number of Trips`, name = "Trips per Day") |> 
  mutate(`% of trips per day` = round(`Number of Trips` / `Trips per Day`, 2))
```

## Output

::: panel-tabset
## Table

```{r}
#| echo: false
output
```

## Summary

```{r}
#| echo: false
skimr::skim(output)
```
:::
