# Week 2

## Requirements

-   [Input the data set](https://drive.google.com/file/d/1AdfaMvu7Wy9osNfIcOuOiLeZE4hk1vDc/view?usp=sharing)

    -   Removing any unnecessary fields (parental fields) will make this challenge easier to see what is happening at each step

-   Format the pupil's name in *First Name Last Name* format (ie Carl Allchin)

-   Create the date for the pupil's birthday in calendar year 2022 (not academic year) ([*link*](https://www.preppindata.com/howto/how-to-use-date-functions))

-   Work out what day of the week the pupil's birthday falls on ([*link*](https://www.preppindata.com/howto/how-to-create-date-parts))

    -   Remember if the birthday falls on a Saturday or Sunday, we need to change the weekday to Friday

-   Work out what month the pupil's birthday falls within

-   Count how many birthdays there are on each weekday in each month ([*link*](https://www.youtube.com/watch?v=zsoJgLRdKjs))

    -   Note: there is an issue with my output as I use the birthday month rather than the 2022 date of the birthday (thanks Rosario). Output updated 17/1/22 9:45 PM GMT)

-   [Output the data](https://drive.google.com/file/d/13XzvSduJIrVh9n3PBHz3S2Nt66vb86UY/view?usp=sharing)

## Setup

```{r}
#| message: false
library(tidyverse)
raw <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1SXZMY-kVx2Dz5q3DoFtqO7JRr3u8rGRF_-vE0lwii3I")
```

## EDA

::: panel-tabset
## Table

```{r}
#| echo: false
raw
```

## Summary

```{r}
#| echo: false
skimr::skim(raw)
```
:::

## Preppin

```{r}
raw |> 
  transmute(
    "Pupil's Name" = paste(`pupil first name`, `pupil last name`),
    `Date of Birth` = as_date(`Date of Birth`),
    "This Year's Birthday" = 
  )
```

## Output

::: panel-tabset
## Table

```{r}
#| echo: false
output
```

## Summary

```{r}
#| echo: false
skimr::skim(output)
```
:::
