# Week 1

## Requirements

-   Input the csv file (link above) ([*help*](https://www.youtube.com/watch?v=V_8Kb8qEtKY&list=PL_t5OlLHbVGzjl3ygGsOnXbr9sxPOrogY)*)*

-   Form the pupil's name correctly for the records in the format *Last Name, First Name* ([*help*](https://www.preppindata.com/howto/how-to-use-string-functions)*)*

-   Form the parental contact's name in the same format as the pupil's 

    -   The Parental Contact Name 1 and 2 are the first names of each parent.

    -   Use parental contact column to select which parent first name to use along with the pupil's last name

-   Create the email address to contact the parent using the format *Parent First Name.Parent Last Name\@Employer.com*

-   Create the academic year the pupils are in ([*help*](https://www.preppindata.com/howto/how-to-use-date-functions))

    -   Each academic year starts on 1st September.

    -   Year 1 is anyone born after 1st Sept 2014 

    -   Year 2 is anyone born between 1st Sept 2013 and 31st Aug 2014 etc

-   Remove any unnecessary columns of data ([*help*](https://www.preppindata.com/howto/how-to-filter)*)*

-   Output the data ([*help*](https://www.youtube.com/watch?v=Rw4dT69aeXk&list=PL_t5OlLHbVGzjl3ygGsOnXbr9sxPOrogY&index=9))

## Setup

```{r}
#| message: false
library(tidyverse)
raw <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1SXZMY-kVx2Dz5q3DoFtqO7JRr3u8rGRF_-vE0lwii3I")
```

## EDA

::: panel-tabset
## Table

```{r}
#| echo: false
raw
```

## Summary

```{r}
#| echo: false
skimr::skim(raw)
```
:::

## Preppin

```{r}
calc_year <- \(date, ref = ymd("2014-09-01")){
  ceiling((interval(date, ref) / years(1)) + 1)
}
```

```{r}
output <- raw |>
  mutate(pc = if_else(
    `Parental Contact` == 1,
    `Parental Contact Name_1`,
    `Parental Contact Name_2`
    )
    ) |> 
  transmute(
    "Academic Year" = calc_year(`Date of Birth`),
    "Pupil's Name" = paste0(`pupil last name`, ", ", `pupil first name`),
    "Parental Contact Full Name" = paste0(`pupil last name`, ", ", pc),
    "Parental Contact Email Address" = paste0(pc, ".", `pupil last name`, "@", `Preferred Contact Employer`, ".com")
    )
```

## Output

::: panel-tabset
## Table

```{r}
#| echo: false
output
```

## Summary

```{r}
#| echo: false
skimr::skim(output)
```
:::
