# Week 8

## Requirements

-   [Import the data](https://docs.google.com/spreadsheets/d/1kb5IkxQlJoWKGPVxmHb_D7POaAKFXUl8/edit?usp=sharing&ouid=113142875990517226017&rtpof=true&sd=true) (excel file)

-   From pkmn_stats dataset remove the columns height, weight and evolves from

-   Pivot (wide to long) pkmn stats so that hp, attack, defense, special_attack, special_defense, and speed become a column called 'combat_factors'

-   Using the evolutions data look up the combat_factors for each Pokémon at each stage, making sure that the combat_factors match across the row, i.e. we should be able to see the hp for Bulbasaur, Ivysaur and Venusaur on one row

-   Remove any columns for 'pokedex_number' and 'gen_introduced' that were from joins at Stage 2 & 3

-   If a Pokémon doesn't evolve remove it from the dataset

-   Find the combat power values relating to the Pokémon's last evolution stage

-   Sum together each Pokémon's combat_factors

-   Find the percentage increase in combat power from the first & last evolution stage

-   Sort the dataset, ascending by percentage increase

    -   If using Tableau Prep, consider introducing a field to manage this sort and then hide it

-   [Output the data](https://drive.google.com/file/d/11xpzmV2zNjE95P9qCU65ygyuzfZXgour/view?usp=sharing)

-   Which Pokémon stats decrease from evolving?

## Setup

```{r}
#| message: false
#| results: hide
library(tidyverse)
googledrive::drive_download("https://docs.google.com/spreadsheets/d/1kb5IkxQlJoWKGPVxmHb_D7POaAKFXUl8")
stats <- readxl::read_xlsx("input_pkmn_stats_and_evolutions.xlsx", sheet = "pkmn_stats")
evolutions <- readxl::read_xlsx("input_pkmn_stats_and_evolutions.xlsx", sheet = "pkmn_evolutions")
file.remove("input_pkmn_stats_and_evolutions.xlsx")
```

## EDA

::: panel-tabset
## Table 1

```{r}
#| echo: false
stats
```

## Summary 1

```{r}
#| echo: false
skimr::skim(stats)
```

## Table 2

```{r}
#| echo: false
evolutions
```

## Summary 2

```{r}
#| echo: false
skimr::skim(evolutions)
```
:::

## Preppin

```{r}
output <- evolutions |> 
  filter(!is.na(Stage_2)) |> 
  mutate(final_evol = coalesce(Stage_3, Stage_2)) |> 
  left_join(
    stats |> 
      transmute(
        name, pokedex_number, gen_introduced,
        initial_combat_power = rowSums(across(hp:speed))),
    by = c("Stage_1" = "name")
  ) |> 
  left_join(
    stats |> 
      transmute(name, final_combat_power = rowSums(across(hp:speed))),
    by = c("final_evol" = "name")
  ) |> 
  mutate(combat_power_increase = (final_combat_power - initial_combat_power) / initial_combat_power) |> 
  arrange(combat_power_increase) |> 
  select(-final_evol)
```

## Output

::: panel-tabset
## Table

```{r}
#| echo: false
output
```

## Summary

```{r}
#| echo: false
skimr::skim(output)
```
:::
