# Week 5

## Requirements

-   [Input the data](https://drive.google.com/file/d/1CQtCut8yFplIC85lWHKB6Fk3GvTyoXK0/view?usp=sharing)

-   Divide the students grades into 6 evenly distributed groups (have a look at 'Tiles' functionality in Prep)

    -   By evenly distributed, it means the same number of students gain each grade within a subject

-   Convert the groups to two different metrics:

    -   The top scoring group should get an A, second group B etc through to the sixth group who receive an F

    -   An A is worth 10 points for their high school application, B gets 8, C gets 6, D gets 4, E gets 2 and F gets 1.

-   Determine how many high school application points each Student has received across all their subjects 

-   Work out the average total points per student by grade 

    -   ie for all the students who got an A, how many points did they get across all their subjects

-   Take the average total score you get for students who have received at least one A and remove anyone who scored less than this. 

-   Remove results where students received an A grade (requirement updated 2/2/22)

-   How many students scored more than the average if you ignore their As?

-   [Output the data](https://drive.google.com/file/d/1YfMdlBejnH_x2-B1Cp0UEci09pPM6jxQ/view?usp=sharing)

::: callout-warning
## Different Results

We were confused by the instructions. We were also unable to reach exactly the same averages and therefore the output is not identical to the one published. If you have an idea why, please share.
:::

## Setup

```{r}
#| message: false
library(tidyverse)
raw <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1WTx9htqDaBXFr-p23MbLbe-Rk9FMJzLpuYHUFOZ60aw")
```

## EDA

::: panel-tabset
## Table

```{r}
#| echo: false
raw
```

## Summary

```{r}
#| echo: false
skimr::skim(raw)
```
:::

## Preppin

```{r}
mid <- raw |> 
  pivot_longer(-`Student ID`, names_to = "Subject", values_to = "Score") |> 
  mutate(Grade = LETTERS[7 - ntile(Score, 6)], .by = "Subject") |> 
  mutate(
    Points = case_match(
      Grade,
      "A" ~ 10,
      "B" ~ 8,
      "C" ~ 6,
      "D" ~ 4,
      "E" ~ 2,
      "F" ~ 1
    )
    ) |> 
  mutate(`Total points per Student` = sum(Points), .by = `Student ID`) |> 
  mutate(`Avg student total points per grade` = 
           round(mean(`Total points per Student`) ,2),
         .by = Grade)

avg_a <- mid |> 
  filter(Grade == "A") |> 
  slice(1) |> 
  pull(`Avg student total points per grade`)

output <- mid |> 
  filter(`Total points per Student` >= avg_a, Grade != "A")
```

## Output

::: panel-tabset
## Table

```{r}
#| echo: false
output
```

## Summary

```{r}
#| echo: false
skimr::skim(output)
```
:::
