# Week 3

## Requirements

-   [Input both data sets](https://drive.google.com/drive/folders/1FP9EuxfRjdbhghpdWOp6Oh_MIrUAKklY?usp=sharing)

-   Join the data sets together to give us the grades per student

-   Remove the parental data fields, they aren't needed for the challenge this week

-   Pivot the data to create one row of data per student and subject

-   Rename the pivoted fields to *Subject* and *Score*

-   Create an average score per student based on all of their grades

-   Create a field that records whether the student passed each subject

    -   Pass mark is 75 and above in all subjects

-   Aggregate the data per student to count how many subjects each student passed

-   Round the average score per student to one decimal place

-   Remove any unnecessary fields and [output the data](https://drive.google.com/file/d/1WrsXao4IFq8T6TiTl2YcXDe5XpV2jEk4/view?usp=sharing)

## Setup

```{r}
#| message: false
library(tidyverse)
raw_1 <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1SXZMY-kVx2Dz5q3DoFtqO7JRr3u8rGRF_-vE0lwii3I")
raw_2 <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1K1hnY0htobsvNmmpBrXy7liAEC7AQpZgHkctqN5UrU4")
```

## EDA

::: panel-tabset
## Table 1

```{r}
#| echo: false
raw_1
```

## Summary 1

```{r}
#| echo: false
skimr::skim(raw_1)
```

## Table 2

```{r}
#| echo: false
raw_2
```

## Summary 2

```{r}
#| echo: false
skimr::skim(raw_2)
```
:::

## Preppin

```{r}
output <- raw_1 |>
  select(`Student ID` = id, Gender = gender) |>
  left_join(
    raw_2 |>
      pivot_longer(-`Student ID`, names_to = "Subject", values_to = "Score") |>
      summarize(
        `Passed Subjects` = sum(Score >= 75),
        `Student's Avg Score` = round(mean(Score), 1),
        .by = `Student ID`
      ),
    by = "Student ID"
  ) |>
  select(`Passed Subjects`, `Student's Avg Score`, `Student ID`, Gender)
```

## Output

::: panel-tabset
## Table

```{r}
#| echo: false
output
```

## Summary

```{r}
#| echo: false
skimr::skim(output)
```
:::
