# Week 7

## Requirements

-   [Input the data](https://drive.google.com/drive/folders/1bg9hl-yMKlwNrLwEt_hjHE9LWPuMRK6X?usp=sharing)

-   People, Location, Leader, and Dates:

    -   Join the People, Location, and Leader data sets together

    -   Remove the location id fields, the secondary leader id field

    -   Create last name, first name fields for the agent and the leader

    -   Limit the dates to just 2021 and join those to the People, Location, Leader step

    -   Keep the id, agent name, leader 1, leader name, month start date, join, and location field

-   Monthly Data

    -   union the worksheets in the input step

    -   merge the mismatched fields

    -   create a month start date

    -   remove the table names and file paths field

    -   join the data with the people - remember we need to show every agent for every month

-   Goals

    -   add the goals input to the flow

    -   clean the goal data to have the goal name & numeric value

    -   add the goals to the combined people & data step

    -   be sure that you aren't increasing the row count - the goals should be additional columns

-   Metrics & Met Goal Flags

    -   create a calculation for the percent of offered that weren't answered (for each agent, each month)

    -   create a calculation for the average duration by agent (for each agent, each month)

    -   create a calculation that determines if the sentiment score met the goal

    -   create a calculation that determines if the not answered percent met the goal

-   [Output the data](https://drive.google.com/file/d/1i1BO524Su6N4sMTiN_gOMb-3-FkpTUeK/view?usp=sharing)

::: callout-warning
## Number of Rows

The output given here results in 1,516 rows instead of 1,620 given in the official solution
:::

## Setup

```{r}
#| message: false
#| results: hide
library(tidyverse)
library(readxl)
googledrive::drive_download("https://docs.google.com/spreadsheets/d/1zj-Tk5WiXwiBpZwagJ1r93pLVK-1gUlo")
googledrive::drive_download("https://docs.google.com/spreadsheets/d/1ivu8S2WxkdXG2Ake2fez8l40MJ-lxrsC")
```

```{r}
read_metrics <- function(file){
  sheet_names <- excel_sheets(file)
  lookup <- c(
    "Calls Offered" = "Offered",
    "Calls Not Answered" = "Not Answered",
    "Calls Answered" = "Answered"
  )
  map(sheet_names, ~read_xlsx(file, sheet = .x) |> 
        rename(any_of(lookup))) |> 
    set_names(sheet_names)
}

metrics <- read_metrics("MetricData2021.xlsx") |> 
  list_rbind(names_to = "Month")
```

```{r}
people <- read_xlsx("PeopleData.xlsx", sheet = "People") 
leaders <- read_xlsx("PeopleData.xlsx", sheet = "Leaders")
locations <- read_xlsx("PeopleData.xlsx", sheet = "Location") 
```

```{r}
file.remove("PeopleData.xlsx", "MetricData2021.xlsx")
```

## EDA

::: panel-tabset
## Table 1

```{r}
#| echo: false
metrics
```

## Summary 1

```{r}
#| echo: false
skimr::skim(metrics)
```

## Table 2

```{r}
#| echo: false
people
```

## Summary 2

```{r}
#| echo: false
skimr::skim(people)
```

## Table 3

```{r}
#| echo: false
leaders
```

## Table 4

```{r}
#| echo: false
locations
```
:::

## Preppin

```{r}
output <- people |> 
  left_join(
    leaders,
    by = c("Leader 1" = "id"), 
    suffix = c("_agent", "_leader")
    ) |> 
  left_join(
    locations,
    by = c("Location ID")
    ) |> 
  left_join(
    metrics,
    by = c("id" = "AgentID")
  ) |> 
  transmute(
    id,
    `Agent Name` = paste(last_name_agent, first_name_agent, sep = ", "),
    `Leader 1`,
    `Leader Name` = paste(last_name_leader, first_name_leader, sep = ", "),
    `Month Start Date` = ymd(paste("2021", Month, "01")),
    Location, 
    `Calls Answered`,
    `Calls Not Answered`,
    `Not Answered Rate` = round(`Calls Not Answered` / `Calls Offered`, 3),
    `Not Answered Percent < 5` = 5,
    `Met Not Answered Rate` = `Not Answered Rate` < `Not Answered Percent < 5` / 100,
    `Total Duration`,
    `Agent Avg Duration` = round(`Total Duration` / `Calls Answered`),
    Transfers,
    Sentiment,
    `Sentiment Score >= 0` = 0,
    `Met Sentiment Goal` = Sentiment >= `Sentiment Score >= 0`
  )
```

## Output

::: panel-tabset
## Table

```{r}
#| echo: false
output
```

## Summary

```{r}
#| echo: false
skimr::skim(output)
```
:::
